Classical density functional theory for the square-well liquid

### 2014-05-27 papers/square-well-liquid/paper.tex
Added Barker and Henderson citations for their square well work.  Added parts of derivations we have done but commented them out pending better organization. Tested on knightley. Took 1:06.49.
Added some perturbation theory stuff to square well paper Tested on knightley. Took 0:28.95.

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/periodic-ww130-ff30-N200-E.pdf}
  \caption{A simple DOS plot!}
\end{figure}

>>>>

%%Stuff commented out below was me typing out this section before I
%%realised we had something like this.  I'm leaving the code here for now.

%% If we take into account
%% the $\beta$ term then $a_2$ becomes
%% \begin{align}\label{eq:A2-exact}
%%   A_2 &= \int \int \textrm{d$\rr_1$
%%     d$\rr_2$}n(\rr_1)n(\rr_2)g^{(2)}(\rr_1\,\rr_2)\Phi(r_{12})
%% \end{align}
%% We want to use our approximation for $g^{(2)}$
%% written as Eqn. \ref{eq:g2-our-mean}:
%% \begin{align}
%%   g^{(2)}(\rr_1,\rr_2) \approx 
%%   \frac{g_s \left(\rr_{12},g_{\sigma}(\rr_1)\right) + g_s
%%     \left(\rr_{12},g_{\sigma}(\rr_2)\right)}{2}.
%% \end{align}
%% If the look at the homogeneous case then
%% \begin{align}
%%   g_s \left(\rr_{12},g_{\sigma}(\rr_1)\right) = g_s
%%   \left(\rr_{21},g_{\sigma}(\rr_2)\right).
%% \end{align}
%% With which we can rewrite equation \ref{eq:A1-exact} to be  
%% \begin{align}
%%   A_2 &= \int \int \textrm{d$\rr_1$
%%     d$\rr_2$}n(\rr_1)n(\rr_2)g_s(\rr_{12}\,g_\sigma(\rr_1))\Phi(r_{12}).
%% \end{align}
%% We can write $g_s$ as a sum of functions
%% \begin{align}\
%%   g_s(\rr_{12}\,g_\sigma(\rr_1)) = \sum_i f_i(r_{12})G_i(g_\sigma)
%% \end{align}
%% where the ith function we assume is a product of two functions that explicitly
%% depend on $r_{12}$ and $g_\sigma(\rr_1)$ respectively.

\subsection{Local-compressibility approximation}

Barker and Henderson presented two approximations for the second order
term in the inverse temperature expansion, one of which they name the
local-compressiblitity
approximation. \cite{barker2004perturbationSW,barker2004perturbationII}
\fixme{below is some perturbation theory stuff}
We start with the definition for the Helmholtz free energy of the
reference system and add a correction to the energy due to a perturbation correction:
\begin{align}
  A &= A_{ref}+A_a \\
  &=-kT \ln \left( \sum_i e^{-\beta [E_{ref}(i) + \lambda E_a(i)]}
  \right).
\end{align}
Take the derivative at $\lambda = 0$:
\begin{align}
  \frac{\partial A}{\partial \lambda} \bigg{|}_{\lambda = 0} &= -kT
  \frac{\sum_i -\beta E_a(i) e^{-\beta [E_{ref}(i) + \lambda E_a(i)]}}{\sum_i e^{-\beta
      [E_{ref}(i) + \lambda E_a(i)]}} \\
  &= \frac{\sum_i E_a(i) e^{-\beta [E_{ref}(i) + \lambda E_a(i)]}}{\sum_i e^{-\beta
      [E_{ref}(i) + \lambda E_a(i)]}} \\
  &= \sum_i E_{a,i}{P_i}|_{\lambda = 0}.
\end{align}
Then we take the second derivative;
\begin{align}
  \frac{\partial^2 A}{\partial \lambda^2} \bigg{|}_{\lambda = 0} &=
  \sum_i E_{a,i} \frac{\partial P_i}{\partial
    \lambda}\bigg{|}_{\lambda = 0} \\
  &= \sum_i E_{a,i}\Bigg[ \frac{-\beta E_a(i)e^{-\beta [E_{ref}(i) +
        \lambda E_a(i)]}}{\sum_j e^{-\beta [E_{ref}(j) + \lambda E_a(j)]}}
  \notag \\
  &- \frac{e^{-\beta [E_{ref}(i) + \lambda
        E_a(i)]}\sum_k -\beta E_a(k)e^{-\beta [E_{ref}(k) + \lambda
        E_a(k)]}}{\left( \sum_j e^{-\beta [E_{ref}(j) + \lambda
        E_a(j)]} \right)^2} \Bigg] \\
  &= \sum_i E_a(i)\bigg[ -\beta E_a(i)P_i + \beta P_i \sum_j
  E_a(j)P_j \bigg] \\
  &= -\beta \sum_i E_a^2(i)P_i + \beta \sum_i P_i E_a(i)\sum_j E_a(j)
  P_j \\
  &= -\beta \sum_i E_a^2(i)P_i + \beta \bigg(\sum_i E_a(i)P_i\bigg)^2
\end{align}
Since we set $\lambda = 0$, the probabilities are over the reference state so these become
averages over those states.
\begin{align}
  \frac{\partial^2 A}{\partial \lambda^2} \bigg{|}_{\lambda = 0} &=
  -\beta \left( \left< E_a^2 \right>_0 - {\langle E_a \rangle}_0^2 \right)
\end{align}
%% Our derivation for this looks something like this:
%% \begin{align}
%%   A_2 &\approx -\left(\frac{\partial n}{\partial p}\right)
%%   \int\textrm{d$\rr'$} \notag \\
%%   &\times \frac{\delta}{\delta n(\rr')} \int \int
%%   \textrm{d$\rr_1$ d$\rr_2$} \left[n(\rr_1)
%%   n(\rr_2)g^{(2)}(\rr_1\,\rr_2)\Phi(r_{12})^2 \right]
%% \end{align}
%% \begin{align}
%%   A-A_{ref} &= -kT \ln \left(\frac{Z_a}{Z_{ref}}\right) 
%%   \\ &= -kT \ln \left( \frac{\sum_i e^{-\beta[E_{ref}(i) + \lambda
%%         E_a(i)]}} {\sum_i e^{-\beta E_{ref}(i)}} \right) \\
%% \end{align}
%% Since our perturbed Energy $E_a$ is caused by some small potential
%% $u_a$, we can expand $\exp(-\beta \lambda u_a)$ in a power series.
%% This makes
%% \begin{align}
%%   A-A_{ref} &= -kT \ln \bigg{\langle} 1 - \beta
%%   \lambda u_a + \frac{1}{2} \beta^2 \lambda^2 u_a^2 + \cdots \bigg{\rangle}_0
%% \end{align}
%% Here, the average is over the reference energies.  Now we can expand
%% the the natural log in a series
%% \begin{align}
%%   A-A_{ref} &= -kT \ln \bigg{\langle} 1 - \beta
%%   \lambda u_a + \frac{1}{2} \beta^2 \lambda^2 u_a^2 + \cdots \bigg{\rangle}_0
%% \end{align}

@@

%% \begin{figure}
%%   \includegraphics[width=\columnwidth]{figs/periodic-ww130-ff30-N200-E.pdf}
%%   \caption{A simple DOS plot!}
%% \end{figure}
